An Open Platform for Managing Short Programming Exercises

### 2013-06-24 paper/paper.tex
working on pilot studies section

\begin{table*}
\centering
\begin{tabular}{llll}
\toprule
Institution & Course & Language & Enrollment\\
\midrule
Canisius College & CS-1 & C++ & 30\\
York College & CS-1 & C & 120\\
Knox College & CS-1 & Java & 23\\
University of Auckland & Programming for Engineers & C & 30\\
\bottomrule
\end{tabular}
\caption{CloudCoder pilot studies.}
\label{tab:courses}
\end{table*}

@@

We piloted CloudCoder at several institutions during the 2012-2013
academic year.  Table~\ref{tab:courses} shows a breakdown of the
courses.  We tried to use CloudCoder at Auckland in Fall 2012 for a
course with 700 students, but the free-tier of Amazon EC2 did not
scale up well enough, so we only recorded partial data.  We have made
significant improvements since then and plan to deploy CloudCoder for
the same large course in Fall 2013.

In the Winter 2013 term at Knox College, students taking CS-1 used {\tt CloudCoder}
%
% TODO: \cite{Hovemeyer:2013:CBC:2445196.2445451}.  
% 
We collected over 6,000 submissions
for 32 exercises by 23 students.  We expect to have a much larger
dataset from 120 students at 
York College 
once the Spring 2013 semester ends.  Our analysis of these datasets is
very preliminary at this point, but work is ongoing.

@@

%CS-1 at 

>>>>

\begin{table*}
\centering
\begin{tabular}{llll}
\toprule
Institution & Course & Language & Enrollment\\
\midrule
Canisius College & CS1 & C++ & 30\\
York College & CS1 & C & 122\\
Knox College & CS1 & Java & 23\\
University of Auckland & Programming for Engineers & C & 30\\
\bottomrule
\end{tabular}
\caption{CloudCoder pilot studies.}
\label{tab:courses}
\end{table*}

@@

We piloted CloudCoder at several institutions during the 2012-2013
academic year.  Table~\ref{tab:courses} shows a breakdown of the
courses.  We also tried to use CloudCoder at the University of Auckland in Fall 2012 for a
course with 700 students, but we encountered performance issues
which prevented a full deployment.  We are working on scalability
improvements, and we plan to deploy CloudCoder for
the same large course in Fall 2013.

In the Winter 2013 term at Knox College, students taking CS1 used {\tt CloudCoder}.
We collected over 6,000 submissions
for 32 exercises by 23 students. [TODO: what else?]

In the Spring 2013 term at York College, we used CloudCoder in a CS1
class, taught in C, with 122 students.  There were more than 56,000
submissions for 68 exercises.  Because using CloudCoder was the
only change in pedagogy compared to previous offerings of the course,
we plan to analyze this data to see if we can find evidence that
the exercises resulted in improved outcomes.

%We expect to have a much larger
%dataset from 120 students at 
%York College 
%once the Spring 2013 semester ends.  Our analysis of these datasets is
%very preliminary at this point, but work is ongoing.

@@

%CS1 at 
